A Spatial AR System for Wide-area Axis-aligned Augmentation of Planar Scenes in Industrial Settings

### 2021-06-22 paper/elsarticle/elsarticle-template.tex
paper

%% Group authors per affiliation:
\author{Michael Horn\'{a}\v{c}ek}
\author{Hans K\"{u}ffner-McCauley}
\author{Sebastian Schlund}
\address{Human Centered Cyber Physical Production and Assembly Systems, Institute for Management Sciences, TU Vienna, Austria}

@@

We propose a system that produces the effect of keystone correction analytically, and that intuitively places the desired augmentations in a manner aligned with the axes of an image of the scene acquired by a camera. Moreover, our system is able to handle a projector equipped with a steerable mirror, enabling wide-area factory floor augmentation exceeding the projector's own immediate field of view.
\end{abstract}

@@

We recover the scene plane via spatial resection by applying a PnP algorithm \cite{terzakis2020consistently} to the with respect to 2D-3D correspondences of a chessboard pattern. Note that this step is separate from camera calibration, yet could well be carried out using the same pattern used in the camera calibration step.\footnote{The critical point is that the pattern should ideally be coplanar with the local scene plane, meaning its height above the scene plane should not exceed a few millimeters.} While a single image of such a chessboard pattern placed on the floor could be sufficient if the floor is even, we place a chessboard pattern in close proximity to the projected circles pattern in each projector calibration image in order to recover the scene plane locally to each target location, in order to account for the possibility of an uneven floor.

The pose (i.e., position and orientation) of the projector, for each projector calibration image, is provided alongside $\mathtt{K}_\text{proj}$ by the aforementioned optimization. Note that for a fixed projector with steerable mirror, given a projector calibration image, the recovered projector's pose is the pose the projector would have to have had to project to the given target location \textit{in the absence of the mirror}.

@@

>>>>

%% Group authors per affiliation:
\author{Michael Horn\'{a}\v{c}ek}\corref{mycorrespondingauthor}
\cortext[mycorrespondingauthor]{Corresponding author}
\ead{michael.hornacek@tuwien.ac.at}
\author{Hans K\"{u}ffner-McCauley}
\author{Sebastian Schlund}
\address{Human Centered Cyber Physical Production and Assembly Systems, Institute for Management Sciences, TU Vienna, Austria}

@@

We propose a system that produces the effect of keystone correction analytically, and that intuitively places the desired augmentations in a manner aligned with the axes of an image of the scene acquired by a camera. Moreover, our system is able to handle a projector equipped with a steerable mirror, enabling wide-area factory floor augmentation exceeding the bounds of the projector's own immediate field of view.
\end{abstract}

@@

We recover the scene plane via spatial resection by applying a PnP algorithm \cite{terzakis2020consistently} to the with respect to 2D-3D correspondences of a chessboard pattern. Note that this step is separate from camera calibration, yet could well be carried out using the same calibration pattern used in the camera calibration step.\footnote{The critical point is that the pattern should ideally be coplanar with the local scene plane, meaning its height above the scene plane should not exceed a few millimeters.} While a single image of such a chessboard pattern placed on the floor could be sufficient if the floor is even, we place a chessboard pattern in close proximity to the projected circles pattern in each projector calibration image in order to recover the scene plane locally to each target location, in order to account for the possibility of an uneven floor.

The pose (i.e., position and orientation) of the projector, for each projector calibration image, is provided alongside $\mathtt{K}_\text{proj}$ by the aforementioned optimization procedure. Note that for a fixed projector with steerable mirror, given a projector calibration image, the recovered projector's pose is the pose the projector would have to have had to project to the given target location \textit{in the absence of the mirror}. As this is sufficient for our needs in Section~\ref{sec:approach:homography}, it is in this sense that our system is able to handle a projector equipped with a steerable mirror, without need for modeling the steerable mirror explicitly.

@@

We presented a system that produces the effect of keystone correction analytically, and that intuitively places the desired augmentations in a manner aligned with the axes of an image of the scene acquired by a camera. Moreover, we showed our system to be able to handle a projector equipped with a steerable mirror, enabling wide-area factory floor augmentation exceeding the bounds of the projector's own immediate field of view. Our evaluation demonstrated ...
